2.4 PRNT50

### 2025-07-03 2_scripts/2.4 PRNT50.qmd
Redo figures in pdf

tb_abbs_melt<-reshape2::melt(select(tb_abbs, -c(2:4)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")
```

@@

tb_APLCBS2<-rbind.data.frame(tb_abbs_melt, tb_ros_melt)
rm(tb_abbs, tb_abbs_melt, tb_ros, tb_ros_melt)

@@

tb_APLCBS2$COI_ty[tb_APLCBS2$COI %in% c("50", "0.8")]<-"Positivity"
tb_APLCBS2$COI_ty[tb_APLCBS2$COI %in% c("402.36", "178.81")]<-"Immunity"
```

```{r}
# ggplot
p09.lab<-c("APL (PRNT-50 cutoff)", "CBS (PRNT-50 cutoff)", 
           "APL (manufacturer cutoff)", "CBS (manufacturer cutoff)")
p09c<-tb_APLCBS2 %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(study, COI_ty),
                                    linetype=interaction(study, COI_ty))) +
  geom_point() +
  geom_line()  +
  theme_bw() +
  xlab("Time of Sample Collection") + 
  ylab("Proportion")+ 
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p09.lab)+
  scale_linetype_manual("", values=c(3,3,1,1), labels = p09.lab)+
  ggtitle("Unstratified")
#  theme(legend.position="top")+
#  guides(color = guide_legend(nrow = 2))

@@

```{r}
# Use figure to present data
p13.lab <- c("CBS Raw: Anti-S(+) N(-)", "CBS Transformed: Anti-S(+) N(-)", 
             "APL Raw: Anti-S(+) N(-)", "APL Transformed: Anti-S(+) N(-)")
p13<-dta.vax.2 %>%
  ggplot(aes(x=samplemonth, y=prop.vax, colour=data, linetype=data)) +
  geom_point() +
  geom_line()  +
  theme_bw() + 
  ylim(0,1)+
  ylab("Vaccinated%") +
  scale_colour_manual("", values = c("blue", "brown", "purple","green"),
                      labels = p13.lab)+
  scale_linetype_manual("", values=c(3,3,3,3), labels = p13.lab)+
  theme(legend.position = c(0.8,0.2))
p13
```
##### Print p12 and p13 together
```{r}
p1213<-plot_grid(p12 + xlab ("Time of Sample Collection") +
                 coord_cartesian(xlim=as.yearmon(c("Oct 2020", "Feb 2023")))+
                 theme(legend.position = c(0.67,0.25)), 
                 p13 + xlab ("Time of Sample Collection") + ylab("") +
                 coord_cartesian(xlim=as.yearmon(c("Oct 2020", "Feb 2023")))+
                 theme(legend.position = c(0.65,0.2)),
                 labels = c("A", "B"),
                 nrow=1,  align = "h")
p1213

png(file="../4_output/figs/Fig.S2 Vax.png", 
    width=2400, height=1200, res=300)
p1213
dev.off()
```

@@

png(file="../4_output/figs/Fig.4 Immunity.png", 
    width=2400, height=2000, res=300)
p09all
dev.off()
```
## 5. Additional analysis for manuscript

>>>>

tb_abbs_melt<-reshape2::melt(select(tb_abbs, 
                                    samplemonth, prop.abbs1, prop.abbs2), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")
```

@@

tb_APLCBS2<-rbind.data.frame(tb_abbs_melt, tb_ros_melt)
#rm(tb_abbs, tb_abbs_melt, tb_ros, tb_ros_melt)

@@

tb_APLCBS2$COI_ty[tb_APLCBS2$COI %in% c("50", "0.8")]<-"Positivity"
tb_APLCBS2$COI_ty[tb_APLCBS2$COI %in% c("402.36", "178.81")]<-"Immunity"

tb_APLCBS2<-tb_APLCBS2 %>%
  mutate(prop=as.numeric(prop))
```

```{r}
# ggplot
p09.lab<-c("APL (PRNT-50 cutoff)", "CBS (PRNT-50 cutoff)", 
           "APL (manufacturer cutoff)", "CBS (manufacturer cutoff)")
p09c<-tb_APLCBS2 %>%
  filter(!is.na(COI_ty)) %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(study, COI_ty))) +
  geom_point() +
  geom_line(aes(linetype = interaction(study, COI_ty)))  +
  theme_bw() +
  xlab("Time of Sample Collection") + 
  ylab("Proportion")+ 
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p09.lab)+
  scale_linetype_manual("", values=c(3,3,1,1), labels = p09.lab)+
  ggtitle("Unstratified")
#  theme(legend.position="top")+
#  guides(color = guide_legend(nrow = 2))

@@

```{r}
# Use figure to present data
p13.lab <- c("CBS Raw: Anti-S(+) N(-)", "CBS Transformed: Anti-S(+) N(-)", 
             "APL Raw: Anti-S(+) N(-)", "APL Transformed: Anti-S(+) N(-)")
p13<-dta.vax.2 %>%
  ggplot(aes(x=samplemonth, y=prop.vax, colour=data, linetype=data)) +
  geom_point() +
  geom_line()  +
  theme_bw() + 
  ylim(0,1)+
  ylab("Vaccinated%") +
  scale_colour_manual("", values = c("blue", "brown", "purple","green"),
                      labels = p13.lab)+
  scale_linetype_manual("", values=c(3,3,3,3), labels = p13.lab)+
  theme(legend.position = c(0.8,0.2))
p13
```

##### Print p12 and p13 together
```{r}
p1213<-plot_grid(p12 + xlab ("Time of Sample Collection") +
                 coord_cartesian(xlim=as.yearmon(c("Oct 2020", "Feb 2023")))+
                 theme(legend.position = c(0.67,0.25)), 
                 p13 + xlab ("Time of Sample Collection") + ylab("") +
                 coord_cartesian(xlim=as.yearmon(c("Oct 2020", "Feb 2023")))+
                 theme(legend.position = c(0.65,0.2)),
                 labels = c("A", "B"),
                 nrow=1,  align = "h")
p1213

png(file="../4_output/figs/Fig.S2 Vax.png", 
    width=2400, height=1200, res=300)
p1213
dev.off()
```
##### Print p12 and p13 in pdf formats, as requested by AJE
```{r}
ggsave(file="../4_output/figs/Fig.S2 Vax.pdf", 
       width=2400, height=1200, dpi=300, units = "px", 
       plot = p1213)
```

@@

ggsave(file="../4_output/figs/Fig.3 Immunity.pdf",
       plot = p09all,
        width=2400, height=2000, 
        dpi=300, units ="px")
```
## 5. Additional analysis for manuscript
